---
title: "COVID19 Africa Report"
output: 
  html_document:
    df_print: paged
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, cache = T, warning = F,
                      message = F)
```

This report show....

It includes data from... to ....


### Time series of input data


```{r ts_cases, cache=F}
library(dplyr)
library(plotly)
library(shiny)
library(plotly)
library(ggplot2)

all_input <- readRDS("inputs/all_input.rds") %>% 
  select(-geom)

name_vars <- c("observed" = "Daily cases", 
               "rp100k" = "Daily cases per 100,000",
               "sindex" = "Stringency Index",
               "testing" = "Testing",
               "temp" = "Temperature",
               "rain" = "Rainfall",
               "sh" = "Humidity")

inputPanel(
  selectInput("var", label = "Select variable:",
              choices = c("Daily cases" = "observed", 
                          "Daily cases per 100,000" = "rp100k",
                          "Stringency Index" = "sindex",
                          "Testing" = "testing",
                          "Temperature" = "temp",
                          "Rainfall" = "rain",
                          "Humidity" = "sh")),
  selectInput("country", label = "Select country:",
              choices = unique(all_input$COUNTRY), 
              multiple = T)
)

renderPlotly({
  all_input %>%
  filter(COUNTRY %in% input$country) %>% 
  plot_ly(x = ~ time, y = ~ eval(as.name(input$var)), color = ~ COUNTRY,
          type = "scatter", mode = "lines") %>%
  layout(xaxis = list(title = ""),
         yaxis = list(title = name_vars[[input$var]],
                      hoverformat = ".2f"),
         hovermode = "compare")
})


```


### Spatial distribution of cumulative number of cases


```{r map, out.width="100%"}
library(sf)
library(leaflet)
library(leafem)

counts <- readRDS("inputs/daily_cases_plot.rds")
source("R/functions.R")

cases_total <- reshape_df(counts, "observed") %>%
  group_by(COUNTRY) %>%
  summarise(total = sum(observed))

africa <- st_read("inputs/africa_plot.gpkg", quiet = T)

africa <- africa %>%
  inner_join(cases_total, by = c("name" = "COUNTRY"))

africa$rpk100 <- (africa$total / africa$Pop2020) * 100000


pal <- colorQuantile(palette = "RdYlBu", n = 10,
                     domain = africa$rpk100, reverse = T)

labF <- function(type, cuts, p) {
    n = length(cuts)
    paste0(round(cuts[-n]), " &ndash; ", round(cuts[-1]))
  }

labels <- sprintf("<strong> %s </strong>
                  : %s",
                  as.character(africa$name),
                  round(africa$rpk100)) %>%
  lapply(htmltools::HTML)

leaflet() %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addPolygons(data = africa,
    color = "grey", weight = 1,
    fillColor = ~ pal(rpk100), fillOpacity = 0.5,
    highlightOptions = highlightOptions(color = "black", weight = 3),
    label = labels,
    labelOptions = labelOptions(
      style = list(
        "font-weight" = "normal",
        padding = "3px 8px"
      ),
      textsize = "15px", direction = "auto"
    )
  ) %>%
  addLegend(data = africa, pal = pal, values = ~ rpk100, opacity = 0.5,
            labFormat = labF,
            title = "Total number of</br>cases per 100,000", position = "bottomleft")
 # addHomeButton(ext = raster::extent(africa), layer.name = "Africa")
```

# Model output

**Table 1: Maximum likelihood estimates and corresponding 95% confidence intervals for a model with 7-day lag.** For climatic variables, a 1 standard deviation increase in climatic variables results in the shown relative risk.  For stringency index, a 10% increase in stringency is associated with the increased relative risk shown. HDI and testing policy are on ordinal scale 0 to 3 (HDI) and 0 to 4 (testing policy). Estimates that are statistically significant are highlighted in green. The spatial weight decay, $\rho$, reflects the strength of inter-country connectivity, and overdispersion parameter, $\psi$.

```{r tab_params}
fit <- readRDS("inputs/fitted_model_LAG7_RE.rds")

beta_hat <- fit$coefficients[1:16]
sd_hat <- fit$se[1:16]

zscores <- beta_hat / sd_hat
pvalues <- 2 * pnorm(abs(zscores), lower.tail = F)
pvalues <- as.character(ifelse(pvalues < 0.001, "< 0.001", round(pvalues, 3))) 
pvalues <- ifelse(nchar(pvalues) < 5, paste0(pvalues, 0), pvalues)
pvalues <- tibble(Params = names(beta_hat), pvalues)

tab <- readr::read_csv("inputs/tab_params_LAG7_RE.csv") %>% 
  left_join(pvalues)

tab <- tab[c(16, 9, 1:8, 15, 10:14, 17, 18), ]
tab$pvalues[c(1, 2, 11, 17:18)] <- "-"
tab[, 2:4] <- apply(tab[,2:4], 2, 
                    function(x) ifelse(nchar(x) < 5, paste0(x, 0), x))

tab$Params <- c("Intercept", "Intercept", "log(population)", "HDI",
                "Landlocked", "Stringency$_{t-7}$", "Testing$_{t-7}$",
                "Rain$_{t-7}$", "Temperature$_{t-7}$", "Humidity$_{t-7}$",
                "Intercept", "log(population)",
                "HDI", "Landlocked", "Stringency$_{t-7}$", "Testing$_{t-7}$", 
                "$\\rho$", "$\\psi$")

CI <- paste0("(", tab$`2.5 %`, ", ", tab$`97.5 %`, ")")
tab$`97.5 %` <- NULL
tab$`2.5 %` <- CI
names(tab)[3] <- "CI"
boldID <- which(tab$pvalues == "< 0.001" | as.numeric(tab$pvalues) <= 0.1)

library(knitr)
library(kableExtra)

kbl(tab, col.names = c("Parameter", "Relative Risk", "95% CI", "p-value"), 
    align = c("lccc"), ) %>% 
  kable_material(full_width = T, font_size = 20) %>% 
  row_spec(0, bold = T) %>% 
  row_spec(boldID, background = "#cdf7d6", color = "Black") %>% 
  pack_rows("Endemic", 1, 1, background = "#e8e8e8") %>% 
  pack_rows("Within-country", 2, 10, background = "#e8e8e8") %>% 
  pack_rows("Between-country", 11, 16, background = "#e8e8e8") %>% 
  pack_rows("", 17, 18, background = "#e8e8e8")
  
```

# Predictions

```{r preds, cache = F}

all_preds <- readr::read_csv("inputs/predictions.csv")

inputPanel(
  selectInput("ctr", label = "Select country:",
              choices = unique(all_preds$cname))
)

renderPlotly({
  all_preds %>%
    filter(cname == input$ctr) %>% 
    plot_preds()
})

```

